---
title: "Power with RMSEA and Monte Carlo Simulation"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Compute Power for RMSEA 

Using http://www.quantpsy.org/rmsea/rmsea.htm

From McCallum et al., 1996:
All power estimates are based on alpha = .05. For the test of close fit. e0 = 0.05 and ea = 0.08, where e0 is the null value of the root-mean-square error of approximation (RMSEA) and ea is the alternative value of RMSEA. For the test of not-close fit, e0 = 0.05 and ea = 0.01. For the test of exact fit, e0= 0.00 and ea = 0.05.(http://dx.doi.org.proxy.lib.duke.edu/10.1037/1082-989X.1.2.130)


```{r}

#Power analysis for CSM

alpha <- 0.05 #alpha level
d <- 187 #degrees of freedom
n <- 200 #sample size
rmsea0 <- 0.05 #null hypothesized RMSEA
rmseaa <- 0.08 #alternative hypothesized RMSEA

#Code below this point need not be changed by user
ncp0 <- (n-1)*d*rmsea0^2
ncpa <- (n-1)*d*rmseaa^2

#Compute power
if(rmsea0<rmseaa) {
    cval <- qchisq(alpha,d,ncp=ncp0,lower.tail=F)
    pow <- pchisq(cval,d,ncp=ncpa,lower.tail=F)
}
if(rmsea0>rmseaa) {
    cval <- qchisq(1-alpha,d,ncp=ncp0,lower.tail=F)
    pow <- 1-pchisq(cval,d,ncp=ncpa,lower.tail=F)
}
print(pow)


```

# Compute power with Monte Carlo simulation

We'll be using the package called simsem. If it's not already installed in your computer, you'll need to install it with the code below.
You'll need to load the library for a package every time you open a new R session. Once the session is open and you've loaded them once, you don't need to load them again (unless you close the app)

```{r}
install.packages("simsem")
library(simsem)
library(lavaan)
```

Steps: 

1. Read the dataset

```{r}
data <- read.table('ex12.7real.dat')
data <- read.csv('ex12.7real.csv') # if reading the csv version

```

2. Let's give our variables names

```{r}
colnames(data) <- c('y1',
                    'y2',
                    'y3',
                    'y4',
                    'y5',
                    'y6',
                    'y7',
                    'y8',
                    'y9',
                    'y10',
                    'x1',
                    'x2')
```

3. Specify the population model with starting values

```{r}
popmodel <- 'f1 =~ start(1)*y1 + start(1)*y2 + start(1)*y3 + start(1)*y4 + start(1)*y5 # Latent varible f1 #factor f1 is composed of y1-y5 indicators
          f2 =~ start(1)*y6 + start(1)*y7 + start(1)*y8 + start(1)*y9 + start(1)*y10 # Latent variable f2 #factor f2 is composed of y6-y10 indicators
          
          f1~~start(0.5)*f1 # Variance f1
          f2~~start(0.5)*f2 # Variance f2
          
          f1~~start(0.25)*f2 # Covariance between f1 and f2
          
          y1~~start(0.5)*y1 # Residual variance y1
          y2~~start(0.5)*y2 # Residual variance y2 (and so on)
          y3~~start(0.5)*y3
          y4~~start(0.5)*y4
          y5~~start(0.5)*y5
          
          y1 ~ start(1)*1 # Intercept (mean) y1 - we indicate this with ~ 1
          y2 ~ start(1)*1 # Intercept (mean) y2 (and so on)
          y3 ~ start(1)*1
          y4 ~ start(1)*1
          y5 ~ start(1)*1
          
          y6~~start(0.75)*y6 # Residual variance y6
          y7~~start(0.75)*y7 # Residual variance y7 (and so on)
          y8~~start(0.75)*y8
          y9~~start(0.75)*y9
          y10~~start(0.75)*y10
          
          y6 ~ start(2)*1 # Intercept (mean) y6 - we indicate this with ~ 1
          y7 ~ start(2)*1 # Intercept (mean) y7 (and so on)
          y8 ~ start(2)*1 
          y9 ~ start(2)*1 
          y10 ~ start(2)*1 
          
          f1 ~  start(0.3)*x1 + start(0.5)*x2 # Regressing f1 on x1 and x2
          f2 ~  start(0.5)*x1 + start(0.3)*x2 # Regressing f2 on x1 and x2
          '
```

4. Fit the population model

```{r}

popfit <- sem(popmodel, # Name of our model
              data = data) # Name of our dataframe

fitest <- parameterEstimates(popfit) # Ask for output with estimates of fit and create dataframe with values
fitest # view dataframe of population values (note that these match Mplus's)

```

5. We now specify the analysis model 

```{r}

analysismod <- 'f1 =~  y1 + y2 + y3 + y4 + y5 
                f2 =~  y6 + y7 + y8 + y9 + y10
          
                f1 ~  x1 + x2
                f2 ~  x1 + x2

                y1 ~ 1
                y2 ~ 1
                y3 ~ 1
                y4 ~ 1
                y5 ~ 1
                y6 ~ 1
                y7 ~ 1
                y8 ~ 1                
                y9 ~ 1
                y10 ~ 1'

```

6. And we fit it to the simulation using the sim() function

```{r}

sim <- sim(nRep = 500, # number of random samples
           model = analysismod, # sample model that we're trying to fit
           generate = popfit, # fitted population estimates
           n = 500, # sample size
           lavaanfun = "sem", # lavaan function we're using
           seed = 45335) # set the seed (very useful for replication)
```

