---
title: "Complex Measurement Models - MMTM Test for Construct Validity - NTCM"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(lavaan)
```

## Part 2: MTMM(Multitrait-multimethod models) Models

This script is a continuation of the "CTCM 2022.Rmd", in which we estimated a CTCM We are now estimating an NTCM, in which we exclude all latent variables referent to traits, but keep those referent to methods. 

## No Traits/Correlated Methods (NTCM)

```{r}
mtmm_data <- read.table("ind7mt.dat")
```

```{r}
colnames(mtmm_data) <- c(
  'scself',
  'sctch',
  'scpar',
  'scpeer',
  'acself',
  'actch',
  'acpar',
  'acpeer',
  'ecself',
  'ectch',
  'ecpar',
  'ecpeer',
  'mcself',
  'mctch',
  'mcpar',
  'mcpeer'
)
```

## Model Specification

In the CTCM, the model indicated a negative variance for the observed variable ACSELF. This could be an indication that the variance should be fixed to 0 (this is especially appropriate if the variance is small and not significantly different from zero). To address this issue, we fix the variance of ACSELF to 0 in this model.

```{r}
mtmm_ntcm <- '
# Latent factors

# F1-F4 are latent methods (parent, teacher, self, peer report)
# In this model, we do not include these factors
# F1 =~ NA*scself + sctch + scpar + scpeer
# F2 =~ NA*acself + actch + acpar + acpeer
# F3 =~ NA*ecself + ectch + ecpar + ecpeer
# F4 =~ NA*mcself + mctch + mcpar + mcpeer

# F5-F8 are latent traits (social, academic, english, math competence)
F5 =~ NA*scself + acself + ecself + mcself
F6 =~ NA*sctch + actch + ectch + mctch 
F7 =~ NA*scpar + acpar + ecpar + mcpar
F8 =~ NA*scpeer + acpeer + ecpeer + mcpeer

# Latent variable variances fixed to 1
# F1 ~~ 1*F1
# F2 ~~ 1*F2
# F3 ~~ 1*F3
# F4 ~~ 1*F4

F5 ~~ 1*F5
F6 ~~ 1*F6
F7 ~~ 1*F7
F8 ~~ 1*F8

# Covariances between latent methods and latent traits fixed to 0

acself ~~ 0*acself
'
```

## Fitting the model

```{r}

mtmm_ntcm_fit <- cfa(model = mtmm_ntcm,
               data = mtmm_data,
               missing = "ml",
               estimator = "mlr",
               control = list(iter.max = 1000)
               )

```

Note that the error in the model is gone this time. However, the fit is still poor. As noted in the Mplus output, this is good, as it indicates that a model that accounts only for the methods (but not the traits) is not a good fit to the data.

## Model Output 

### Model summary

```{r}
summary(mtmm_ntcm_fit, 
        standardized = TRUE, 
        rsquare = TRUE,
        fit.measures = TRUE)
```

From the output, we can see that the residual variance of ACSELF is negative, which is causing errors in the model.

Also note in the output that the variance of ACSELF is 0, as we fixed it in the model specification portion.
